% list of fontawesome icons available here: http://ftp.cc.uoc.gr/mirrors/CTAN/fonts/fontawesome/doc/fontawesome.pdf
%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.1.3, 30 April 2017) written by
% LianTze Lim (liantze@gmail.com), based on the 
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you want to use \orcid or the
%% academicons icons, add "academicons"
%% to the \documentclass options. 
%% Then compile with XeLaTeX or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper]{altacv}

%% AltaCV uses the fontawesome and academicon fonts
%% and packages. 
%% See texdoc.net/pkg/fontawecome and http://texdoc.net/pkg/academicons for full list of symbols.
%% When using the "academicons" option,
%% Compile with LuaLaTeX for best results. If you
%% want to use XeLaTeX, you may need to install
%% Academicons.ttf in your operating system's font %% folder.


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Change the font if you want to.

% If using pdflatex:
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{arabtex}
\usepackage{soul}
\usepackage{hyperref}
\usepackage{qrcode}
% If using xelatex or lualatex:
% \setmainfont{Lato}

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{3E0097}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=VividPurple,
}
% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
\addbibresource{sample.bib}
\begin{document}
\name{Fatima Carolina Bdeir}
\tagline{BSc Computer Science, AUB, Dec 2018. Minor in Creative Writing}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0

\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{fatima.c.bdeir@gmail.com}
  \phone{+961 (71) 559-949}
  \mailaddress{Beirut, LEBANON}
  \linkedin{linkedin.com/in/fbdeir}
  \github{github.com/fbdeir} % I'm just making this up though.
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}
\cvevent{Junior Software Engineer}{Monty Mobile}{May 2019 - Present}{Beirut, Lebanon}
\begin{itemize}
    \item Unit and integration tests using Junit 4 and 5, as well as containerized tests.
    \item Created an API server to perform business and database logic with OAuth2.0.
    \item Developed a library to send and receive SMS messages using Cloudhopper (SMPP) and Spring.
    \item Developed a library to en-queue and de-queue messages to and from RabbitMq using Spring Boot.
    \item Developed a library to create RestTemplate beans to allow easier and cleaner API calls in other projects.
    \item Developed a git pre-commit hook to enforce a common codestyle.
    \item Applied continuous integration by testing, packaging, and staging merged projects on the pipeline to servers.
    \item Software documentation and ER diagrams to propose a database structure for reverse engineered code.\\
\cvtagpurple{Java} \cvtagpurple{Spring Boot} \cvtagpurple{Linux Commands} \cvtagpurple{Linux servers} \cvtagpurple{systemctl} \cvtagpurple{SMPP} \cvtagpurple{Maven} \cvtagpurple{PostgreSQL} \cvtagpurple{MySQL} \cvtagpurple{Rest APIs} \cvtagpurple{Checkstyle} \cvtagpurple{Junit} \cvtagpurple{Docker/Containerized Tests} \cvtagpurple{Git} \cvtagpurple{MyBatis} \cvtagpurple{Bitbucket} \cvtagpurple{Gitlab} \cvtagpurple{RabbitMq}


\divider

   
    
\end{itemize}
\cvevent{Internship - Artificial Intelligence Developer}{Murex}{July 2018}{Beirut, LEBANON}
\begin{itemize}
\item Member of a team that developed chatbot applications using various artificial intelligence technologies and software architectures.\\
\cvtagpurple{C\#}
\cvtagpurple{xUnit}
\cvtagpurple{Microsoft Bot Framework}
\cvtagpurple{LUIS}
\cvtagpurple{DialogFlow}

\end{itemize}

\divider

\cvevent{Internship - Artificial Intelligence Developer}{CardioDiagnostics}{June 2018}{Beirut, LEBANON}
\begin{itemize}
\item Research different methods to automate electrocardiogram  (ECG) classification using machine learning and feature extraction, then training of a neural network to classify different cardiac arrhythmias.\\
\cvtagpurple{AzureML}
\cvtagpurple{Python}
\cvtagpurple{Azure virtual machines}
\cvtagpurple{Keras}
\cvtagpurple{Tensorflow}
\end{itemize}

\cvsection{Projects}
\cvachievement{\qrcode[height=0.25in]{https://goo.gl/jQLUm2}
\qquad}{ASKI}{An Amazon Alexa skill to query AUB course offering.}

\begin{itemize}
    \item Stored course data in NoSQL DynamoDB on AWS cloud, then wrote AWS Lambda functions written in Javascript using Nodejs\\
    \cvtagpurple{AWS Lambda} 
\cvtagpurple{Alexa Skills Kit} 
\cvtagpurple{AWS DynamoDb}
\end{itemize}
\divider

\cvachievement{\faHeartbeat}{TBear}{A mobile application for reporting Tuberculosis Bumps.}
\begin{itemize}
    \item Done with the supervision of the head of family medicine at AUBMC Dr. Ghassan Hamadeh.
    \item Created Lambda functions on AWS in Python accessed through the Amazon API Gateway.
    \item Took part in the image processing development using the OpenCV library.\\
    \cvtagpurple{OpenCV}
\cvtagpurple{AWS EC2} 
\cvtagpurple{Javascript}
\cvtagpurple{Python}

\end{itemize}

\end{document}
